---
title: "Temperature Map, Germany"
author: "Ummehani"
date: "October 25, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Temperature Map of Germany

Based on 2016 Temparture Data

ISO code of Germany, DEU; Data aquired from= "getData"

Level of boundary, 1

Temperature Data aquired from = "worldclim", tmean, tmax, tmin

Longitute, 10;

Latiture, 51;

Resolution, 0.5

## Map of Germany

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(raster)
germany <- getData("GADM", country="DEU", level=1) # make the country boundary
plot(germany) #plot germany
```

## Mean Annaul Temperature of Germany

```{r}
temp <- getData("worldclim", var="tmean", res=0.5, lon=10, lat=51) # data acquisition for temp mean
plot(temp) # plot the tmean graph
```

## Maximum Annual Temperature of Germany

```{r}
temp_max <- getData("worldclim", var="tmax", res=0.5, lon=10, lat=51) # data acquisition for temp mean
plot(temp_max) # plot the tmean graph
```

## Minimum Annual Temperature of Germany

```{r}
temp_min <- getData("worldclim", var="tmin", res=0.5, lon=10, lat=51) # data acquisition for temp mean
plot(temp_min) # plot the tmean graph
```

## Map of Mean Temperature (Cropping)

```{r}
temp_ger1 <- crop(temp, germany) # crop to extent map of germany
spplot(temp_ger1) # plot crop output
```

## Map of Mean Temperature (Masking)

```{r}
temp_ger2 <- mask(temp_ger1, germany) # mask to shape the map of germany
spplot(temp_ger2) # plot the output
```


## Map of Max Temperature (Cropping)

```{r}
temp_ger3 <- crop(temp_max, germany) # crop to extent map of germany
spplot(temp_ger3) # plot crop output
```

## Map of Max Temperature (Masking)

```{r}
temp_ger4 <- mask(temp_ger3, germany) # masking to shape map of germany
spplot(temp_ger4) #plot the result
```


## Map of Min Temperature (Cropping)

```{r}
temp_ger5 <- crop(temp_min, germany) # crop to extent map of germany
spplot(temp_ger5) # plot crop output
```

# Map of Min Temperature (Masking)

```{r}
temp_ger6 <- mask(temp_ger5, germany) # masking to shape map of germany
spplot(temp_ger6) #plot the result
```

## Map of Max Temperature

```{r}
temp_ger4 <- mask(temp_ger3, germany) # masking to shape map of germany
spplot(temp_ger4) #plot the result
```

## Map of Mean Temperature

```{r}
temp_ger2 <- mask(temp_ger1, germany) # mask to shape the map of germany
spplot(temp_ger2) # plot the output
```

## Map of Min Temperature

```{r}
temp_ger6 <- mask(temp_ger5, germany) # masking to shape map of germany
spplot(temp_ger6) #plot the result
```

